---
title: "Final_Analysis"
author: "Alexis Porter"
date: "8/26/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Construct 2X2 matrix based on sensitivity/specificity scores

|        Tested          |  SZ| CON| 
|:-----------------|----:|---:|
|SZ         | $TP$|   $FP$|  
|Con     | $FN$|   $TN$|  
|Total       | $n_{SZ}$|   $n_{CON}$|  


$TP = Sensitivity*n_{SZ}$ \
$FP = n_{CON}*(1-Specificity)$ \
$FN = n_{SZ} - TP$ \
$TN = n_{CON} - FP$ \

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(data.table)
library(patchwork)
library(car)
library(cutpointr)
library(tidyverse)
library(ggplot2)
library(metafor)
library(scales)
library(dplyr)
# Load dataset set categorical variables as such
#Including a few more Ariana found
meta_df=read_csv('~/Desktop/meta_analysis/meta_R_MeanMerge_etal_updated.csv') %>%
  mutate(imaging = factor(imaging, levels = c("T1", "DTI", "FC", "Multimodal")),  
         mL_method = factor(mL_method),
         imaging_spec = factor(imaging_spec),
         reporting_validation_set = factor(reporting_validation_set),
         names = Study,
         names(names), 
         TP = round(sensitivity * n1),
         FP = round(n2*(1-specificity)),
         FN = n1 - TP,
         TN = n2 - FP,
         N = n1 + n2)
meta_df$tpr = tpr(meta_df$TP, meta_df$FN)
meta_df$fpr = fpr(meta_df$FP, meta_df$TN)
meta_df = meta_df[order(meta_df$imaging, 5000-meta_df$Year),]


# remove outliers based on eggers
egger_rem <- meta_df %>%
  filter(flagged_outlier == 0)


both <- meta_df %>%
  filter(imaging == 'Multimodal')
DTI <- meta_df %>%
  filter(imaging == 'DTI')
FC <- meta_df %>%
  filter(imaging == 'FC')
T1 <- meta_df %>%
  filter(imaging == 'T1')  


year_pub<- meta_df %>%
  filter(Year > 2010)  


#motion contamination FC only studies
motionFC=read_csv('~/Desktop/meta_analysis/FC_only_analysis.csv') %>%
  mutate(imaging_codedR = factor(imaging_codedR),
         mL_method = factor(mL),
         CV = factor(CV),
         Atlas = factor(Atlas),
         Atlas_type = factor(Atlas_type),
         GSR = factor(GSR, levels = c(0,1), labels = c('No','Yes')),
         names = Coded_inR,
         names(names))

motionFC <- motionFC %>%
  mutate(TP = round(Sensitivity * Scz),
         FP = round(HC*(1-Specificity)),
         FN = Scz - TP,
         TN = HC - FP,
         N = Scz+HC)
motionFC <-  motionFC[!(motionFC$names=="Zhu2018" | motionFC$names=="Tang2012"|  motionFC$names=="Liu2020" | motionFC$names=="Serin2021" | motionFC$names=="Lei2020_2"| motionFC$names=="Yu2013"),]
motionFC$n <- motionFC$Scz + motionFC$HC
motionFC$tpr <- tpr(motionFC$TP, motionFC$FN)
motionFC$fpr <- fpr(motionFC$FP, motionFC$TN)


```

```{r}
#Description of means and std 
meta_df %>%
  group_by(imaging) %>%
  summarise_at(vars(sensitivity), list(name = mean))

meta_df %>%
  group_by(imaging) %>%
  summarise_at(vars(specificity), list(name = mean))

#Standard deviation
meta_df %>%
  group_by(imaging) %>%
  summarise_at(vars(sensitivity), list(name = sd))

meta_df %>%
  group_by(imaging) %>%
  summarise_at(vars(specificity), list(name = sd))
```

<br>
Code to see what study's are outliers
```{r, warning=FALSE,message=FALSE, fig.width=10, fig.height=7}
ggplot(meta_df, aes(fpr, tpr)) +
  geom_point(aes(fill = factor(imaging), size = N), colour = 'black',shape = 21, alpha = .6) +
  xlim(0, 1) +
  ylim(0,1) + 
  labs(size = 'Sample Size', x = 'False Positive Rate', y = "Sensitivity")+
  #scale_fill_discrete(name = 'Neuroimaging\nMethod', labels = c("DTI", "rs-FC","Multimodal",  "T1"))+
  scale_fill_manual(name = 'Neuroimaging\nMethod', labels = c("T1","DTI", "rs-FC","Multimodal"), values = c( 'blue','green', 'red', 'black')) +
  scale_size(range=c(5,18),breaks=c(25,50,75,100,500,1000),labels=c("25","50","75","100","500",">1000"),guide="legend") +
  geom_abline(coef = c(0,1), lty = 2) +
    theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),legend.text=element_text(size=15), legend.title = element_text(size =20),
        axis.title.x = element_text(size = 30),axis.title.y = element_text(size = 30))   +
  guides(fill = guide_legend(override.aes = list(size = 6)))

#ggsave('~/Desktop/meta_analysis/figures/max_dataset/sensplot_averagemodel.png')
```



```{r,fig.width=30, fig.height=25,warning=FALSE,message=FALSE}
#If this plot looks weird just adjust the fig.width or fig.height columns to make readable 
dat <- escalc(measure="OR", ai=TP, bi=FN, ci=FP, di=TN, data=meta_df,
              slab=paste(Study))


### fit random-effects model
res <- rma(yi, vi, data=dat, measure = "OR")
### a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}
 
### set up forest plot (with 2x2 table counts added; the 'rows' argument is
### used to specify in which rows the outcomes will be plotted)
forest(res, xlim=c(-16, 16),at=c(-0.3,1, 2.35, 4.9, 7.45, 10),efac=c(0,1), #steps = 5,
       ilab=cbind(TP, FN, FP, TN), ilab.xpos=c(-4.5,-3.5,-2.5,-1.5),refline = 1,alim = c(-.3,15), cex.lab = 2,
       cex=2.5, ylim=c(-2, 85), order=order(imaging), rows=c(4:25,29:37,41:67,71:80), #c(4:12, 16:42, 48:57, 62:83),
       mlab=mlabfun("Model for All Studies", res),
       header="Author(s)\nand Year")
# we want to see weighted size psize=1,
### set font expansion factor (as in forest() above) and use a bold font
#op <- par(cex=1.7, font=2)
 
### add additional column headings to the plot
text(c(-4.5,-3.5,-2.5,-1.5), 84, c("TP", "FN", "FP", "TN"), font =2 , cex = 2.5)
text(c(-4,-2), 85.5, c("Scz", "Control"), cex = 2.5, font = 2)
 
### switch to bold italic font
#par(font=4)
 
### add text for the subgroups
text(-16, c(26.1,38.1,68.1, 81.1), font = 2, pos=4, cex = 2.7, c("T1",
                               "DTI",
                               "rs-FC",
                               "Multimodal"))
 
### set par back to the original settings
#par(op)

### fit random-effects model in the three subgroups
res.s <- rma(yi, vi, subset=(imaging=="DTI"), data=dat)
res.r <- rma(yi, vi, subset=(imaging=="FC"), data=dat)
res.a <- rma(yi, vi, subset=(imaging=="Multimodal"),  data=dat) #bottom one is multimodal
res.m <- rma(yi, vi, subset=(imaging=="T1"),  data=dat) #top is T1
 
### add summary polygons for the three subgroups
addpoly(res.m, row=2.5, mlab=mlabfun("Model for T1", res.m), cex = 2.5, efac = 0.5)
addpoly(res.s, row=27.5, mlab=mlabfun("Model for DTI", res.s), cex =2.5,efac = 0.5 )
addpoly(res.r, row= 39.5, mlab=mlabfun("Model for rs-FC", res.r), cex = 2.5,efac = 0.5)
addpoly(res.a, row= 69.5, mlab=mlabfun("Model for Multi", res.a), cex = 2.5,efac = 0.5)
 
### fit meta-regression model to test for subgroup differences
res <- rma(yi, vi, mods = ~imaging, data=dat)
 
### add text for the test of subgroup differences
text(-16, -3, pos=4, cex=2.5, bquote(paste("Test for Subgroup Differences: ",
     Q[M], " = ", .(formatC(res$QM, digits=2, format="f")), ", df = ", .(res$p - 1),
     ", p = ", .(formatC(res$QMp, digits=2, format="f")))))
#dev.off() 
```



<br>
Code for determining outliers

<br>
```{r,warning=FALSE,message=FALSE,fig.width=14, fig.height=10}

library(dmetar)

dat_old <- escalc(measure="OR", ai=TP, bi=FN, ci=FP, di=TN, data=meta_df,
              slab=paste(Study))
dat_old$esse <- sqrt(dat_old$vi)
DTI_t <- dat_old%>%
  filter(imaging == 'DTI')
T1_t <- dat_old %>%
  filter(imaging == 'T1')
FC_t <- dat_old%>%
  filter(imaging == 'FC')
multi_t <- dat_old %>%
  filter(imaging == 'Multimodal')
res.DTI_t <- rma(yi, vi, data=DTI_t, method = 'EE') #to test for homogeneity (equal effects model)
res.FC_t <- rma(yi, vi,     data=FC_t, method = 'EE')
res.multi_t <- rma(yi, vi,  data=multi_t, method = 'EE')
res.T1_t <- rma(yi, vi, data=T1_t, method = 'EE') 



op <- par(mar = c(5,7,6,4) + 0.1, mfrow=c(2,2))
#par(mfrow=c(2,2)) 
funnel(res.T1_t, main="Model for T1", xlab = "",cex.main = 3, cex.lab = 3, cex.axis =2.5)
funnel(res.DTI_t, main="Model for DTI", ylab = "", xlab = "",cex.main = 3, cex.lab = 3, cex.axis =2.5)
funnel(res.FC_t, main="Model for FC" ,cex.main = 3, cex.lab = 3, cex.axis =2.5)
funnel(res.multi_t,  main="Model for Multimodal", ylab = "", cex.main = 3, cex.lab = 3, cex.axis =2.5)

```






Looking through metafor packages there are other ways to evaluate eggers test and macaskills test
Because were interested in publication bias within each imaging type lets run through this 
https://www.rdocumentation.org/packages/metafor/versions/0.5-0/topics/ranktest

Paper that reviews all tests
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6082203/
Peters test

https://jamanetwork.com/journals/jama/fullarticle/202337

An example of a study that uses the peters test
https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1000316

```{r,fig.width=20, fig.height=40,warning=FALSE,message=FALSE}

#removal of outliers 

dat <- escalc(measure="OR", ai=TP, bi=FN, ci=FP, di=TN, data=egger_rem,
              slab=paste(Study))


### fit random-effects model
res <- rma(yi, vi, data=dat, measure = "OR")
### a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}
 
### set up forest plot (with 2x2 table counts added; the 'rows' argument is
### used to specify in which rows the outcomes will be plotted)
forest(res, xlim=c(-38, 20),at=c(-0.2,1, 2.35, 4.9, 7.45, 10), efac=c(0,1), #steps = 5,
       ilab=cbind(TP, FN, FP, TN), ilab.xpos=c(-23,-20,-16,-13),refline = 1,alim = c(-.2,10),
       cex=2, ylim=c(-2, 73), order=c(imaging), rows=c(3:9, 14:36, 41:47, 51:68),
       mlab=mlabfun("Model for All Studies", res),
        header="Author(s)\nand Year")
# we want to see weighted size psize=1,
### set font expansion factor (as in forest() above) and use a bold font
#op <- par(cex=3, font=2)
 
### add additional column headings to the plot
text(c(-23,-20,-16,-13), 72, c("TP", "FN", "FP", "TN"), cex = 2, font = 2)
text(c(-21.5,-14.5),     73.5, c("Scz", "Control"), cex = 2, font = 2)
 
### switch to bold italic font
#par(font=4)
 
### add text for the subgroups
text(-38, c(10,37,48, 69), pos=4, cex = 2, font =2, c("DTI",
                               "FC",
                               "Multimodal",
                               "T1")) #top is T1
 
### set par back to the original settings
#par(op)

### fit random-effects model in the three subgroups
res.s <- rma(yi, vi, subset=(imaging=="DTI"), data=dat)
res.r <- rma(yi, vi, subset=(imaging=="FC"),     data=dat)
res.a <- rma(yi, vi, subset=(imaging=="Multimodal"),  data=dat) #bottom one is multimodal
res.m <- rma(yi, vi, subset=(imaging=="T1"),  data=dat) #top is T1
 
### add summary polygons for the three subgroups
addpoly(res.m, row=49.5, mlab=mlabfun("Model for T1", res.m))
addpoly(res.s, row=1.5, mlab=mlabfun("Model for DTI", res.s))
addpoly(res.r, row= 12.5, mlab=mlabfun("Model for FC", res.r))
addpoly(res.a, row= 38.5, mlab=mlabfun("Model for Multi", res.a))
 
### fit meta-regression model to test for subgroup differences
res <- rma(yi, vi, mods = ~imaging, data=dat)
 
### add text for the test of subgroup differences
text(-38, -3, pos=4, cex=2, bquote(paste("Test for Subgroup Differences: ",
     Q[M], " = ", .(formatC(res$QM, digits=2, format="f")), ", df = ", .(res$p - 1),
     ", p = ", .(formatC(res$QMp, digits=2, format="f")))))
#dev.off() 
```


```{r}
#Evaluating eggers test (regtest function) and Peters test (1/N lm function)
T1_asy <- T1_t %>%
  filter(yi < 3.5)

multi_asy <- multi_t %>%
  filter(vi < 1)

#DTI 
DTI_asy <- DTI_t %>%
  filter(yi < 3)
#FC
FC_asy <- FC_t %>%
  filter(vi < .6 & yi < 4)

regtest(yi,vi, data = T1_asy)
regtest(yi, vi, data = DTI_asy)
regtest(yi, vi, data = T1_t)
regtest(yi, vi, data = DTI_t)
regtest(yi, vi, data = FC_t)
regtest(yi, vi, data = FC_asy)
regtest(yi, vi, data = multi_t)
regtest(yi, vi, data = multi_asy)

### Peters' test (using inverse of total sample size)
summary(lm(yi ~ I(1/N), weights=1/vi, data=DTI_t))
summary(lm(yi ~ I(1/N), weights=1/vi, data=T1_t))
summary(lm(yi ~ I(1/N), weights=1/vi, data=FC_t))
summary(lm(yi ~ I(1/N), weights=1/vi, data=multi_t))

```
we can formally test for funnel asymmetry, by predicting the effect size from its standard error. For this, we can simply apply the regtest function to our existing random-effects meta-analysis, and the SE will be used as a predictor:
If p>.05 the result is non-significant, so there is no evidence for asymmetry. It looks like T1 is the only subset group that is not asymetrical

```{r}
detach("package:metafor", unload=TRUE) 
#sometimes you have to detach package here to get mada to run
```

```{r,warning=FALSE,message=FALSE}
library(mada)


#imaging
fit.imaging.ml <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ imaging, method = "ml")
summary(fit.imaging.ml)

#year
fit.imaging.ml <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ Year, method = "ml")
summary(fit.imaging.ml)

#sample size
fit.imaging.ml <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ n1+n2, method = "ml")
summary(fit.imaging.ml)


#gender
fit.imaging.ml <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ gender_F_n1+gender_F_n2, method = "ml")
summary(fit.imaging.ml)

```
Year of publication excluding old studies

```{r}
#after removing outlier studies 

#imaging
fit.imaging.ml <- reitsma(egger_rem, formula = cbind(tsens, tfpr) ~ imaging, method = "ml")
summary(fit.imaging.ml)

#year
fit.imaging.ml <- reitsma(egger_rem, formula = cbind(tsens, tfpr) ~ Year, method = "ml")
summary(fit.imaging.ml)

#sample size
fit.imaging.ml <- reitsma(egger_rem, formula = cbind(tsens, tfpr) ~ n1+n2, method = "ml")
summary(fit.imaging.ml)


#gender
fit.imaging.ml <- reitsma(egger_rem, formula = cbind(tsens, tfpr) ~ gender_F_n1+gender_F_n2, method = "ml")
summary(fit.imaging.ml)


```





```{r, figures-side,fig.width=25, fig.height=10, dev = "png"}
#fit using reml random effects meta regression
#png(file='~/Desktop/meta_analysis/figures/forestplot_outlier_removed.png')
fit.imaging <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ imaging)

# Fitting the reitsma model with no covariates
fit.reitsma <- reitsma(meta_df)
fit.both <- reitsma(both)
fit.dti <- reitsma(DTI)
fit.fc <- reitsma(FC)
fit.t1 <- reitsma(T1)

par(mfrow=c(1,2), mai = c(1,1.07,1.07,1)) 
#png(file='~/Desktop/meta_analysis/figures/reitsma_plot.png')

plot(fit.reitsma, sroclwd = 4, lwd = 4,
main = "SROC curve (bivariate model)", cex.main = 3.5, cex.lab = 3.5, cex.axis =2.5)
points(fpr(both), sens(both), pch = 2, cex = 3, lwd = 2.5)
points(fpr(FC), sens(FC), pch = 2, col = 'red', cex = 3, lwd = 2.5)
points(fpr(T1), sens(T1), pch = 2, col = 'blue', cex = 3, lwd= 2.5)
points(fpr(DTI), sens(DTI), pch = 2, col = 'green', cex = 3, lwd = 2.5)
legend("bottomright", legend=c("T1","DTI", "rs-FC", "Multimodal",'summary'), pch=c(2,2,2,2,1), lwd = 4, col = c('blue','green','red', 'black', 'black'), cex = 3)
abline(coef = c(0,1), lty = 2)

plot(fit.both, xlim = c(0,.5), ylim = c(0.5,1), cex.main = 3.5, cex.lab = 3.5, cex.axis =2.5, main = "Comparison between neuroimaging methods", lwd = 4)
lines(sroc(fit.dti), lty = 2, col = 'green', lwd = 4)
lines(sroc(fit.fc), lty = 3, col = 'red', lwd = 4)
lines(sroc(fit.t1), lty = 4, col = 'blue', lwd = 4)
ROCellipse(fit.dti, lty = 2, pch = 2, col = 'green',add = TRUE, lwd = 4)
ROCellipse(fit.fc, lty = 3, pch = 2, col = 'red',add = TRUE, lwd = 4)
ROCellipse(fit.t1, lty = 4, pch = 2, col = 'blue',add = TRUE, lwd = 4)
points(fpr(DTI), sens(DTI), pch = 2, col = 'green', cex = 4, lwd = 4)
points(fpr(both), sens(both), pch = 2, cex = 4, lwd = 2)
points(fpr(FC), sens(FC), pch = 2, col = 'red', cex = 4, lwd = 2)
points(fpr(T1), sens(T1), pch = 2, col = 'blue', cex = 4, lwd = 2)
#legend("bottomright", c("DTI", "Multimodal", "FC", "T1"), pch = 2, lty = 1:4, col = c('green', 'black', 'red','blue'), cex = 2)
#dev.off()
```



```{r}
#is there an effect with classification method and imaging modality?

#year of publication
fit.imaging <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ Year*imaging)
summary(fit.imaging)


#gender
fit.imaging <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ gender_F_n1*imaging +gender_F_n2*imaging)
summary(fit.imaging)

#sample size
fit.imaging <- reitsma(meta_df, formula = cbind(tsens, tfpr) ~ n1*imaging+n2*imaging)
summary(fit.imaging)



```
```{r}
#is there an effect with classification method and imaging modality after removing outliers?

#year of publication
fit.imaging <- reitsma(egger_rem, formula = cbind(tsens, tfpr) ~ Year*imaging)
summary(fit.imaging)


#gender
fit.imaging <- reitsma(egger_rem, formula = cbind(tsens, tfpr) ~ gender_F_n1*imaging +gender_F_n2*imaging)
summary(fit.imaging)

#sample size
fit.imaging <- reitsma(egger_rem, formula = cbind(tsens, tfpr) ~ n1*imaging+n2*imaging)
summary(fit.imaging)



```

```{r}
#motion FC analysis 
#total noise
fit.imaging <- reitsma(motionFC, formula = cbind(tsens, tfpr) ~ noise_total)
summary(fit.imaging)
#edges
fit.imaging <- reitsma(motionFC, formula = cbind(tsens, tfpr) ~ factor(motion))
summary(fit.imaging)
#distance
fit.imaging <- reitsma(motionFC, formula = cbind(tsens, tfpr) ~ factor(distance))
summary(fit.imaging)


```
Figures

```{r,fig.width=15, fig.height=5}
p1<-ggplot(year_pub, aes(Year, sensitivity)) +
  geom_point(aes(color = factor(imaging))) +
  geom_smooth(data = year_pub, aes(Year, sensitivity, color = imaging),method = lm, se = FALSE)+
  labs(color = NULL,  x = 'Publication Year', y = "Sensitivity") +
  scale_x_continuous(breaks = seq(2010, 2025, by = 3))+
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20), legend.position = 'none',
        axis.title.x = element_text(size = 25),axis.title.y = element_text(size = 25))  

p2<-ggplot(meta_df, aes(gender_F_n1, fpr, color = imaging)) +
  geom_point() +
  labs(x = 'Psychosis (%F)', y = "FPR(1-Specificity)") +
  scale_color_discrete(name = 'Neuroimaging Group') +
  geom_smooth(data = meta_df, aes(gender_F_n1, fpr, color = imaging),method = lm, se = FALSE)+
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),legend.text=element_text(size=20),legend.title=element_text(size=20),
        axis.title.x = element_text(size = 25),axis.title.y = element_text(size = 25))  





(p1 + p2) + plot_annotation(tag_levels = "A")& theme(plot.tag = element_text(size = 25))
#/(p3 + p4)
ggsave('~/Desktop/meta_analysis/figures/max_dataset/year_gender.png')
```




```{r,fig.width=7, fig.height=4}
#dataset after removing outlier
egger_samples = pivot_longer(egger_rem, cols = c(n1, n2), names_to = 'sample_group', values_to = 'N_sample')

ggplot(egger_samples, aes(N_sample, fpr, color = factor(sample_group))) +
  geom_point(aes(color = factor(sample_group))) +
  geom_smooth(data = egger_samples, aes(N_sample, fpr, color = factor(sample_group)),method = lm, se = FALSE)+
  labs(color = NULL,  x = 'Sample Size', y = "False Positive Rate") +
  scale_color_discrete(name = 'Participant\nGroup', labels = c("Psychosis", 'Healthy Control')) +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 15),axis.text.y = element_text(size = 15), legend.text=element_text(size=15),legend.title=element_text(size=16),
        axis.title.x = element_text(size = 20),axis.title.y = element_text(size = 20))  
ggsave('~/Desktop/meta_analysis/figures/max_dataset/sample_size_egger_remo.png')
```

```{r,fig.width=20, fig.height=13}
#total motion assessment and sample size analysis
df_sample = pivot_longer(meta_df, cols = c(n1, n2), names_to = 'sample_group', values_to = 'N_sample')
#sample size 
p1<-ggplot(df_sample, aes(N_sample, sensitivity)) +
  geom_point(aes(color = factor(sample_group))) +
  geom_smooth(data = df_sample, aes(N_sample, sensitivity, color = factor(sample_group)),method = lm, se = FALSE)+
  labs(color = NULL,  x = 'Sample Size', y = "Sensitivity") +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20), legend.position = 'none',
        axis.title.x = element_text(size = 25),axis.title.y = element_text(size = 30))   

p2<-ggplot(df_sample, aes(N_sample, fpr, color = factor(sample_group))) +
  geom_point(aes(color = factor(sample_group))) +
  geom_smooth(data = df_sample, aes(N_sample, fpr, color = factor(sample_group)),method = lm, se = FALSE)+
  labs(color = NULL,  x = 'Sample Size', y = "False Positive Rate") +
  scale_color_discrete(name = 'Participant\nGroup', labels = c("Psychosis", 'Healthy Control')) +
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20), legend.text=element_text(size=20),legend.title=element_text(size=25),
        axis.title.x = element_text(size = 25),axis.title.y = element_text(size = 30))  

p3 <-
  ggplot(motionFC, aes(fpr, tpr)) +
  geom_point(aes(fill = noise_total, size = n), colour = 'black',shape = 21, alpha = .8) +
  xlim(0, 1) +
  ylim(0,1) +
  labs(size = 'Sample Size', x = 'False Positive Rate', y = "Sensitivity")+
  scale_size(range=c(6,15),breaks=c(25,50,75,100,200,500),labels=c("25","50","75","100","200","500"),guide="legend") +
  geom_abline(coef = c(0,1), lty = 2) +
    scale_fill_gradient2(name = 'Motion\nContamination', limits = c(0,6), breaks = c(1,3,5), 
  low = "black",
  mid = "grey", 
  high = "purple4", midpoint = 3) +
    theme(axis.text.x = element_text(size = 20),
        axis.title.x = element_text(size = 30),
        axis.text.y = element_text(size = 20),
        axis.title.y = element_text(size = 30),
    legend.title=element_text(size=25), 
    legend.text=element_text(size=20)) 


p4<-ggplot() +
  geom_point(data = motionFC, aes(noise_total, fpr, color = process, shape = GSR), size = 5) +
  geom_smooth(data = motionFC, aes(noise_total, fpr),method = lm, se = FALSE)+
  labs(x = 'Motion Contamination Potential', y = 'False Positive Rate')+
  scale_shape_manual(name = "GSR", values = c(19,1))+
  scale_color_discrete(name = "Preprocessing\nMethods") +
  scale_y_continuous(limits = c(0,.75),breaks = seq(0,.7, by =.20), labels = scales::percent_format(scale = 100)) +
  theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25),
        axis.title.y = element_text(size = 30),
            legend.title=element_text(size=25), 
    legend.text=element_text(size=20)) 

(p1+p2)/(p3+p4)+ 
  plot_layout(widths = c(1, 1), heights = unit(c(15, 1), c('cm', 'null')))+ plot_annotation(tag_levels = "A")& theme(plot.tag = element_text(size = 25))
#ggsave('~/Desktop/meta_analysis/figures/max_dataset/sample_size_motion.png')
```


```{r, fig.width=15, fig.height=10}
#boxplots edges and distance contaminated by motion 

p1<-
  ggplot(motionFC, aes(factor(motion), Sensitivity)) +
  geom_boxplot() +
  labs(x = 'Edges Affected by Motion', y = "Sensitivity") +
  scale_y_continuous(limits = c(0.35,1.15),breaks = seq(0.4,1, by =.20), labels = scales::percent_format(scale = 100))+
  theme(legend.position="none", axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 25))  +
  geom_text(x=3, y=1, label="**", size = 20)


p2<-ggplot(motionFC, aes(factor(distance), Sensitivity)) +
  geom_boxplot() +
  labs(x = 'Distance Dependent Effects', y = NULL) +
  scale_y_continuous(limits = c(.35,1.15),breaks = seq(.4,1, by =.20), labels = scales::percent_format(scale=100)) +
  theme(legend.position="none", axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25),axis.title.y = element_text(size = 25))  


p3<-
  ggplot(motionFC, aes(factor(motion), fpr)) +
  geom_boxplot() +
  labs(x = 'Edges Affected by Motion', y = 'FPR(1-Specificity)') +
  scale_y_continuous(limits = c(0,1),breaks = seq(0,.8, by =.20), labels = scales::percent_format(scale = 100))+
  theme(legend.position="none", axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25), axis.title.y = element_text(size = 25))  


p4<-ggplot(motionFC, aes(factor(distance), fpr)) +
  geom_boxplot() +
  labs(x = 'Distance Dependent Effects', y = NULL) +
  scale_y_continuous(limits = c(0,1),breaks = seq(0,.8, by =.20), labels = scales::percent_format(scale=100)) +
  theme(legend.position="none", axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25),axis.title.y = element_text(size = 25))  


(p1+p2)/(p3+p4) + plot_annotation(tag_levels = "A") & theme(plot.tag = element_text(size = 25))


ggsave('~/Desktop/meta_analysis/figures/max_dataset/motion_FCs_figs.png')
```