---
title: "Main"
author: "Alexis Porter"
date: "2022-12-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Construct 2X2 matrix based on sensitivity/specificity scores

|        Tested          |  SZ| CON| 
|:-----------------|----:|---:|
|SZ         | $TP$|   $FP$|  
|Con     | $FN$|   $TN$|  
|Total       | $n_{SZ}$|   $n_{CON}$|  


$TP = Sensitivity*n_{SZ}$ \
$FP = n_{CON}*(1-Specificity)$ \
$FN = n_{SZ} - TP$ \
$TN = n_{CON} - FP$ \

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(data.table)
library(patchwork)
library(car)
library(cutpointr)
library(tidyverse)
library(ggplot2)
library(metafor)
library(scales)
library(dplyr)



# Load dataset set categorical variables as such
# All datasets (even overlapping), external results included
meta_df=read_csv('~/Desktop/meta_analysis/home_response/external.csv') %>%
  mutate(imaging = factor(imaging, levels = c("T1", "DTI", "FC", "Multimodal")),  
         mL_method = factor(mL_method),
         imaging_spec = factor(imaging_spec),
         reporting_validation_set = factor(reporting_validation_set),
         names = Study,
         names(names), 
         TP = round(sensitivity * n1),
         FP = round(n2*(1-specificity)),
         FN = n1 - TP,
         TN = n2 - FP,
         N = n1 + n2)
meta_df$tpr = tpr(meta_df$TP, meta_df$FN)
meta_df$fpr = fpr(meta_df$FP, meta_df$TN)
meta_df = meta_df[order(meta_df$imaging, 5000-meta_df$Year),]
#Remove overlapping datasets since calculating average
#external data
ext_plot <- meta_df %>%
  filter(reporting_validation_set == 1)

external_df <- meta_df %>%
  filter(reporting_validation_set == 1 & imaging == 'FC' | imaging == 'T1')

#External data no outliers
ext_no_outliers <- meta_df %>%
  filter(reporting_validation_set == 1 &  imaging == 'FC' | imaging == 'T1' & flagged_external_outlier == 0)

#Internal training folds 
internal_df=read_csv('~/Desktop/meta_analysis/home_response/internal_training_only.csv') %>%
  mutate(imaging = factor(imaging, levels = c("T1", "DTI", "FC", "Multimodal")),  
         mL_method = factor(mL_method),
         imaging_spec = factor(imaging_spec),
         reporting_validation_set = factor(reporting_validation_set),
         names = Study,
         names(names), 
         TP = round(sensitivity * n1),
         FP = round(n2*(1-specificity)),
         FN = n1 - TP,
         TN = n2 - FP,
         N = n1 + n2)
internal_df$tpr = tpr(internal_df$TP, internal_df$FN)
internal_df$fpr = fpr(internal_df$FP, internal_df$TN)
internal_df = internal_df[order(internal_df$imaging, 5000-internal_df$Year),]

over <- internal_df %>%
  filter(Data_overlap_avg==1) %>%
  mutate(Dataset = factor(Dataset, levels = c("BRNO", "Cobre", "NAMIC", "W. China")),  )
over = over[order(over$Dataset, 5000-over$Year),]


#report training data only and no outliers
internal_df = internal_df %>%
  filter(reporting_validation_set == 0 &  Data_overlap==0)
#report training data only and no outliers
int_no_outliers = internal_df %>%
  filter(overlap_outliers ==0 )



```




```{r}
#Description of means and std 
external_df %>%
  group_by(imaging) %>%
  summarise_at(vars(sensitivity), list(name = mean))

external_df %>%
  group_by(imaging) %>%
  summarise_at(vars(specificity), list(name = mean))

#Standard deviation
external_df %>%
  group_by(imaging) %>%
  summarise_at(vars(sensitivity), list(name = sd))

external_df %>%
  group_by(imaging) %>%
  summarise_at(vars(specificity), list(name = sd))


#Internal folds mean and sd
internal_df %>%
  group_by(imaging) %>%
  summarise_at(vars(sensitivity), list(name = mean))

internal_df %>%
  group_by(imaging) %>%
  summarise_at(vars(specificity), list(name = mean))

internal_df %>%
  group_by(imaging) %>%
  summarise_at(vars(sensitivity), list(name = sd))

internal_df %>%
  group_by(imaging) %>%
  summarise_at(vars(specificity), list(name = sd))
```

<br>

# Comparison Between internal external performance

```{r, warning=FALSE,message=FALSE, fig.width=20, fig.height=7}
p1<- ggplot(internal_df, aes(fpr, tpr)) +
  geom_point(aes(fill = factor(imaging), size = N), colour = 'black',shape = 21, alpha = .6) +
  xlim(0, 1) +
  ylim(0,1) + 
  labs(size = 'Sample Size', x = 'False Positive Rate', y = "Sensitivity", title='Internal Dataset')+
  #scale_fill_discrete(name = 'Neuroimaging\nMethod', labels = c("DTI", "rs-FC","Multimodal",  "T1"))+
  scale_fill_manual(name = 'Neuroimaging\nMethod', labels = c("T1","DTI", "rs-FC","Multimodal"), values = c( 'blue','green', 'red', 'black')) +
  scale_size(range=c(5,18),breaks=c(25,50,75,100,500,1000),labels=c("25","50","75","100","500",">1000"),guide="legend") +
  geom_abline(coef = c(0,1), lty = 2) +
    theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),legend.text=element_text(size=15), legend.title = element_text(size =20),
        axis.title.x = element_text(size = 30),axis.title.y = element_text(size = 30), title=element_text(size=30))   +
  guides(fill = guide_legend(override.aes = list(size = 6)))


p2<- ggplot(ext_plot, aes(fpr, tpr)) +
  geom_point(aes(fill = factor(imaging), size = N), colour = 'black',shape = 21, alpha = .6) +
  xlim(0, 1) +
  ylim(0,1) + 
  labs(size = 'Sample Size', x = 'False Positive Rate', y = "Sensitivity", title = 'External Dataset')+
  #scale_fill_discrete(name = 'Neuroimaging\nMethod', labels = c("DTI", "rs-FC","Multimodal",  "T1"))+
  scale_fill_manual(name = 'Neuroimaging\nMethod', labels = c("T1","DTI", "rs-FC","Multimodal"), values = c( 'blue','green', 'red', 'black')) +
  scale_size(range=c(5,18),breaks=c(25,50,75,100,500,1000),labels=c("25","50","75","100","500",">1000"),guide="legend") +
  geom_abline(coef = c(0,1), lty = 2) +
    theme(axis.text.x = element_text(size = 20),axis.text.y = element_text(size = 20),legend.text=element_text(size=15), legend.title = element_text(size =20),
        axis.title.x = element_text(size = 30),axis.title.y = element_text(size = 30), title=element_text(size=30))   +
  guides(fill = guide_legend(override.aes = list(size = 6)))

p1|p2

#ggsave('~/Desktop/meta_analysis/figures/final/comparison_sensplot.png')
```


<br>

#Code for determining outliers within internal data


```{r,warning=FALSE,message=FALSE,fig.width=10, fig.height=8}

library(dmetar)

dat_old <- escalc(measure="OR", ai=TP, bi=FN, ci=FP, di=TN, data=internal_df,
              slab=paste(Study))
dat_old$esse <- sqrt(dat_old$vi)
DTI_t <- dat_old%>%
  filter(imaging == 'DTI')
T1_t <- dat_old %>%
  filter(imaging == 'T1')
FC_t <- dat_old%>%
  filter(imaging == 'FC')
multi_t <- dat_old %>%
  filter(imaging == 'Multimodal')
res.DTI_t <- rma(yi, vi, data=DTI_t, method = 'EE') #to test for homogeneity (equal effects model)
res.FC_t <- rma(yi, vi,     data=FC_t, method = 'EE')
res.multi_t <- rma(yi, vi,  data=multi_t, method = 'EE')
res.T1_t <- rma(yi, vi, data=T1_t, method = 'EE') 



op <- par(mar = c(4,6,6,4) + 0.1, mfrow=c(2,2))
#par(mfrow=c(2,2)) 
funnel(res.T1_t, main="Model for T1", xlab = "",cex.main = 3, cex.lab = 3, cex.axis =2.5)
funnel(res.DTI_t, main="Model for DTI", ylab = "", xlab = "",cex.main = 3, cex.lab = 3, cex.axis =2.5)
funnel(res.FC_t, main="Model for FC" ,cex.main = 3, cex.lab = 3, cex.axis =2.5)
funnel(res.multi_t,  main="Model for Multimodal", ylab = "", cex.main = 3, cex.lab = 3, cex.axis =2.5)


#Eggers test 
regtest(yi, vi, data = T1_t)
regtest(yi, vi, data = DTI_t)
regtest(yi, vi, data = FC_t)
regtest(yi, vi, data = multi_t)

### Peters' test (using inverse of total sample size)
summary(lm(yi ~ I(1/N), weights=1/vi, data=DTI_t))
summary(lm(yi ~ I(1/N), weights=1/vi, data=T1_t))
summary(lm(yi ~ I(1/N), weights=1/vi, data=FC_t))
summary(lm(yi ~ I(1/N), weights=1/vi, data=multi_t))

#outliers lying 95% pooled estimate
find.outliers(res.DTI_t)
find.outliers(res.FC_t)
find.outliers(res.multi_t)
find.outliers(res.T1_t)
```

# Outliers from external data

```{r}

dat_old <- escalc(measure="OR", ai=TP, bi=FN, ci=FP, di=TN, data=external_df,
              slab=paste(Study))
dat_old$esse <- sqrt(dat_old$vi)

T1_t <- dat_old %>%
  filter(imaging == 'T1')
FC_t <- dat_old%>%
  filter(imaging == 'FC')


res.FC_t <- rma(yi, vi, data=FC_t, method = 'EE')
res.T1_t <- rma(yi, vi, data=T1_t, method = 'EE') 



op <- par(mar = c(4,6,6,4) + 0.1, mfrow=c(1,2))
funnel(res.T1_t, main="Model for T1", xlab = "",cex.main = 3, cex.lab = 3, cex.axis =2.5)
funnel(res.FC_t, main="Model for FC" ,cex.main = 3, cex.lab = 3, cex.axis =2.5)

#Eggers test 
regtest(yi, vi, data = T1_t)
regtest(yi, vi, data = FC_t)

### Peters' test (using inverse of total sample size)
summary(lm(yi ~ I(1/N), weights=1/vi, data=T1_t))
summary(lm(yi ~ I(1/N), weights=1/vi, data=FC_t))

#outliers lying 95% pooled estimate
find.outliers(res.FC_t)
find.outliers(res.T1_t)
```

# Internal metrics after outlier removal

```{r,fig.width=20, fig.height=40,warning=FALSE,message=FALSE}

# Odds ratio model after outlier removal (internal) 

dat <- escalc(measure="OR", ai=TP, bi=FN, ci=FP, di=TN, data=int_no_outliers,
              slab=paste(Study))


### fit random-effects model
res <- rma(yi, vi, data=dat, measure = "OR")
### a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}
 
### set up forest plot (with 2x2 table counts added; the 'rows' argument is
### used to specify in which rows the outcomes will be plotted)
forest(res, xlim=c(-38, 20),at=c(-0.2,1, 2.35, 4.9, 7.45, 10), efac=c(0,1), #steps = 5,
       ilab=cbind(TP, FN, FP, TN), ilab.xpos=c(-23,-20,-16,-13),refline = 1,alim = c(-.2,10),
       cex=2, ylim=c(-2, 52), order=c(imaging), rows=c(3:10, 15:21, 26:38, 43:47),
       mlab=mlabfun("Model for All Studies", res),
        header="Author(s)\nand Year")

 
### add additional column headings to the plot
text(c(-23,-20,-16,-13), 52, c("TP", "FN", "FP", "TN"), cex = 2, font = 2)
text(c(-21.5,-14.5),     53.5, c("Scz", "Control"), cex = 2, font = 2)
 
 
### add text for the subgroups
text(-38, c(11,22,39, 48), pos=4, cex = 2, font =2, c("T1",
                               "DTI",
                               "rs-FC",
                               "Multimodal")) 
 


### fit random-effects model in the three subgroups
res.s <- rma(yi, vi, subset=(imaging=="DTI"), data=dat)
res.r <- rma(yi, vi, subset=(imaging=="FC"),     data=dat)
res.a <- rma(yi, vi, subset=(imaging=="Multimodal"),  data=dat) 
res.m <- rma(yi, vi, subset=(imaging=="T1"),  data=dat) 
 
### add summary polygons for the three subgroups
addpoly(res.m, row=1.5, mlab=mlabfun("Model for T1", res.m))
addpoly(res.s, row=13.5, mlab=mlabfun("Model for DTI", res.s))
addpoly(res.r, row= 24.5, mlab=mlabfun("Model for rs-FC", res.r))
addpoly(res.a, row= 41.5, mlab=mlabfun("Model for Multi", res.a))
 
### fit meta-regression model to test for subgroup differences
res <- rma(yi, vi, mods = ~imaging, data=dat)
 
### add text for the test of subgroup differences
text(-38, -3, pos=4, cex=2, bquote(paste("Test for Subgroup Differences: ",
     Q[M], " = ", .(formatC(res$QM, digits=2, format="f")), ", df = ", .(res$p - 1),
     ", p = ", .(formatC(res$QMp, digits=2, format="f")))))
#dev.off() 
```
# Combined averages 
```{r,fig.width=35, fig.height=25,warning=FALSE,message=FALSE}
#Forest plot after outlier removal
### fit random-effects model
over_Dat = escalc(measure="OR", ai=TP, bi=FN, ci=FP, di=TN, data=over,
              slab=paste(Study))

over_Dat %>%
  mutate(factor(Dataset))
res <- rma(yi, vi, data=over_Dat, measure = "OR")
### a little helper function to add Q-test, I^2, and tau^2 estimate info
mlabfun <- function(text, res) {
   list(bquote(paste(.(text),
      " (Q = ", .(formatC(res$QE, digits=2, format="f")),
      ", df = ", .(res$k - res$p),
      ", p ", .(metafor:::.pval(res$QEp, digits=2, showeq=TRUE, sep=" ")), "; ",
      I^2, " = ", .(formatC(res$I2, digits=1, format="f")), "%, ",
      tau^2, " = ", .(formatC(res$tau2, digits=2, format="f")), ")")))}
 
### set up forest plot (with 2x2 table counts added; the 'rows' argument is
### used to specify in which rows the outcomes will be plotted) 


forest(res, xlim=c(-16, 15),efac=c(0,1), #steps = 5,
       ilab=cbind(TP, FN, FP, TN), ilab.xpos=c(-5.5,-4.5,-3.5,-2.5), alim = c(-1,15), cex.lab = 2,refline = 1, at=c(-1,1, 2.35, 4.9, 7.45, 10),
       cex=3, ylim=c(-5, 21), order=order(Dataset), rows=c(3:5,8:10, 13:14, 17:18),
       mlab=mlabfun("Pooled Estimate", res),header="Author(s)\nand Year", xlab = "")

### add additional column headings to the plot
text(c(-5.5,-4.5,-3.5,-2.5), 20, c("TP", "FN", "FP", "TN"), font =2 , cex = 3)
text(c(-5,-3), 21.5, c("Scz", "Control"), cex = 3.5, font = 2)


 
### add text for the subgroups
text(-16, c(5.6,10.6,14.6, 18.6), font = 2, pos=4, cex = 3, c("BRNO",
                               "Cobre",
                               "NAMIC",
                               "W. China"))
 


### fit random-effects model in the three subgroups
res.s <- rma(yi, vi, subset=(Dataset=="Cobre"), data=over_Dat)
res.r <- rma(yi, vi, subset=(Dataset=="BRNO"), data=over_Dat)
res.a <- rma(yi, vi, subset=(Dataset=="NAMIC"),  data=over_Dat) 
res.m <- rma(yi, vi, subset=(Dataset=="W. China"),  data=over_Dat) #top is T1
 
### add summary polygons for the three subgroups
addpoly(res.s, row=6.5, mlab=mlabfun("Model for Cobre", res.m), cex = 3, efac = 0.5)
addpoly(res.r, row=1.5, mlab=mlabfun("Model for BRNO", res.s), cex =3,efac = 0.5 )
addpoly(res.a, row= 11.5, mlab=mlabfun("Model for NAMIC", res.r), cex = 3,efac = 0.5)
addpoly(res.m, row= 15.5, mlab=mlabfun("Model for W. China", res.a), cex = 3,efac = 0.5)
#addpoly(res, row = 2, mlab=mlabfun("Model for All Studies", res), cex = 3,efac = 0.5)
### fit meta-regression model to test for subgroup differences
#res <- rma(yi, vi, mods = ~imaging, data=dat)

```



```{r}
detach("package:metafor", unload=TRUE) 
#sometimes you have to detach package here to get mada to run
```

#Reitsma test for internal data with outliers

```{r,warning=FALSE,message=FALSE}
library(mada)

#Intercept model
fit.int <- reitsma(internal_df, formula = cbind(tsens, tfpr) ~ 1, method = "ml")

#imaging
fit.imaging.ml <- reitsma(internal_df, formula = cbind(tsens, tfpr) ~ imaging, method = "ml")
anova(fit.imaging.ml, fit.int)

#year
fit.imaging.ml <- reitsma(internal_df, formula = cbind(tsens, tfpr) ~ Year, method = "ml")
anova(fit.imaging.ml, fit.int)

#Diagnosis
fit.imaging.ml <- reitsma(internal_df, formula = cbind(tsens, tfpr) ~ diagnosis, method = "ml")
anova(fit.imaging.ml, fit.int)

#Sample size
fit.imaging.ml <- reitsma(internal_df, formula = cbind(tsens, tfpr) ~ n1+n2, method = "ml")
anova(fit.imaging.ml, fit.int)
summary(fit.imaging.ml)

#More condensed machine learning (linear v non)
fit.imaging.ml <- reitsma(internal_df, formula = cbind(tsens, tfpr) ~ mL, method = "ml")
anova(fit.imaging.ml, fit.int)

#Cross validation
fit.imaging.ml <- reitsma(internal_df, formula = cbind(tsens, tfpr) ~ CV, method = "ml")
anova(fit.imaging.ml, fit.int)

```

#Reitsma check with externaldata with outliers
```{r}
remove.nan = external_df %>% drop_na()
remove.nan$imaging = factor(remove.nan$imaging)

fit.int <- reitsma(remove.nan, formula = cbind(tsens, tfpr) ~ 1, method = "ml")

#imaging
fit.imaging.ml <- reitsma(remove.nan, formula = cbind(tsens, tfpr) ~ imaging, method = "ml")
anova(fit.imaging.ml, fit.int)
#year
fit.imaging.ml <- reitsma(remove.nan, formula = cbind(tsens, tfpr) ~ Year, method = "ml")
anova(fit.imaging.ml, fit.int)
#Sample size
fit.imaging.ml <- reitsma(remove.nan, formula = cbind(tsens, tfpr) ~ n1+n2, method = "ml")
anova(fit.imaging.ml, fit.int)

```

# Internal df after outlier removal
```{r}
fit.int <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ 1, method = "ml")

#imaging
fit.imaging.ml <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ imaging, method = "ml")
anova(fit.imaging.ml, fit.int)
summary(fit.imaging.ml)

#year
fit.imaging.ml <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ Year, method = "ml")
anova(fit.imaging.ml, fit.int)

#Diagnosis
fit.imaging.ml <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ diagnosis, method = "ml")
anova(fit.imaging.ml, fit.int)

#Sample size
fit.imaging.ml <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ n1+n2, method = "ml")
anova(fit.imaging.ml, fit.int)
summary(fit.imaging.ml)
#More condensed machine learning (linear v non)
fit.imaging.ml <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ mL, method = "ml")
anova(fit.imaging.ml, fit.int)
#Cross validation
fit.imaging.ml <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ CV, method = "ml")
anova(fit.imaging.ml, fit.int)

```




#Evaluating imaging modality in more detail


```{r}


#mada output is incompatbile with mult comp so will fit models separately comparing them to 
DTI_FC = int_no_outliers %>% filter(imaging == "DTI" | imaging == "FC")
DTI_T1= int_no_outliers %>% filter(imaging == "DTI" | imaging == "T1")
DTI_mult= int_no_outliers %>% filter(imaging == "DTI" | imaging == "Multimodal")
T1_FC = int_no_outliers %>% filter(imaging == "T1" | imaging == "FC")
T1_mult= int_no_outliers %>% filter(imaging == "T1" | imaging == "Multimodal")
multi_FC = int_no_outliers %>% filter(imaging == "Multimodal" | imaging == "FC")

fit.DTI.FC <- reitsma(DTI_FC, formula = cbind(tsens, tfpr) ~ factor(imaging), method = "ml")
fit.DTI.T1 <- reitsma(DTI_T1, formula = cbind(tsens, tfpr) ~ factor(imaging), method = "ml")
fit.DTI.multi <- reitsma(DTI_mult, formula = cbind(tsens, tfpr) ~ factor(imaging), method = "ml")
fit.T1.FC <- reitsma(T1_FC, formula = cbind(tsens, tfpr) ~ factor(imaging), method = "ml")
fit.T1.multi <- reitsma(T1_mult, formula = cbind(tsens, tfpr) ~ factor(imaging), method = "ml")
fit.multi.FC <- reitsma(multi_FC, formula = cbind(tsens, tfpr) ~ factor(imaging), method = "ml")

summary(fit.DTI.FC)
summary(fit.DTI.T1)
summary(fit.DTI.multi)
summary(fit.T1.FC)
summary(fit.T1.multi)
summary(fit.multi.FC)

p=c(.02,.4,.006,.06,.01,.3)#,.02,.2,.1,.2,.2,1)
adjusted.p <- p.adjust(p, "fdr")
adjusted.p
```

# Internal after Outlier removal

```{r, figures-side,fig.width=25, fig.height=10, dev = "png"}

fit.imaging <- reitsma(int_no_outliers, formula = cbind(tsens, tfpr) ~ imaging)

both <- int_no_outliers %>%
  filter(imaging == 'Multimodal')
DTI <- int_no_outliers %>%
  filter(imaging == 'DTI')
FC <- int_no_outliers %>%
  filter(imaging == 'FC')
T1 <- int_no_outliers %>%
  filter(imaging == 'T1')  
# Fitting the reitsma model with no covariates
fit.reitsma <- reitsma(int_no_outliers)
fit.both <- reitsma(both)
fit.dti <- reitsma(DTI)
fit.fc <- reitsma(FC)
fit.t1 <- reitsma(T1)

par(mfrow=c(1,2), mai = c(1,1.07,1.07,1)) 
#png(file='~/Desktop/meta_analysis/figures/reitsma_plot.png')

plot(fit.reitsma, sroclwd = 4, lwd = 4,
main = "SROC curve (bivariate model)", cex.main = 3.5, cex.lab = 3.5, cex.axis =2.5)
points(fpr(both), sens(both), pch = 2, cex = 3, lwd = 2.5)
points(fpr(FC), sens(FC), pch = 2, col = 'red', cex = 3, lwd = 2.5)
points(fpr(T1), sens(T1), pch = 2, col = 'blue', cex = 3, lwd= 2.5)
points(fpr(DTI), sens(DTI), pch = 2, col = 'green', cex = 3, lwd = 2.5)
legend("bottomright", legend=c("T1","DTI", "rs-FC", "Multimodal",'summary'), pch=c(2,2,2,2,1), lwd = 4, col = c('blue','green','red', 'black', 'black'), cex = 3)
abline(coef = c(0,1), lty = 2)

plot(fit.both, xlim = c(0,.5), ylim = c(0.5,1), cex.main = 3.5, cex.lab = 3.5, cex.axis =2.5, main = "Comparison between neuroimaging methods", lwd = 4)
lines(sroc(fit.dti), lty = 2, col = 'green', lwd = 4)
lines(sroc(fit.fc), lty = 3, col = 'red', lwd = 4)
lines(sroc(fit.t1), lty = 4, col = 'blue', lwd = 4)
ROCellipse(fit.dti, lty = 2, pch = 2, col = 'green',add = TRUE, lwd = 4)
ROCellipse(fit.fc, lty = 3, pch = 2, col = 'red',add = TRUE, lwd = 4)
ROCellipse(fit.t1, lty = 4, pch = 2, col = 'blue',add = TRUE, lwd = 4)
points(fpr(DTI), sens(DTI), pch = 2, col = 'green', cex = 4, lwd = 4)
points(fpr(both), sens(both), pch = 2, cex = 4, lwd = 2)
points(fpr(FC), sens(FC), pch = 2, col = 'red', cex = 4, lwd = 2)
points(fpr(T1), sens(T1), pch = 2, col = 'blue', cex = 4, lwd = 2)
#legend("bottomright", c("DTI", "Multimodal", "FC", "T1"), pch = 2, lty = 1:4, col = c('green', 'black', 'red','blue'), cex = 2)
#dev.off()
```




